### 2018-12-20 manuscript/manuscript.rmd

trees_path = "../trees_new/"
tree_file_names = list.files(path = trees_path, pattern = ".+\\.contree$")

trees = lapply(
	tree_file_names,
	function( tree_file ){
		print(tree_file)
		log_file = sub( "contree$", "log", tree_file )

@@

		base_name = sub( "\\.contree$", "", tree_file )
		elements = strsplit(base_name, "\\.") %>% unlist()
		matrix_name = elements[1]
		model_name = elements[2]

>>>>

trees_path = "../trees_new/"
contree_extension = "treefile"
tree_file_names = list.files(path = trees_path, pattern = str_c( "\\.", contree_extension, "$" ))

trees = lapply(
	tree_file_names,
	function( tree_file ){
		print(tree_file)
		log_file = sub( str_c( contree_extension, "$" ), "log", tree_file )

@@

		if(!file.exists(log_file_path)){
			warning( str_c( "Missong log file: ", log_file_path ) )
			return( NA )
		}

		base_name = sub( str_c( "\\.", contree_extension, "$" ), "", tree_file )
		elements = strsplit(base_name, "\\.") %>% unlist()
		matrix_name = elements[1]
		model_name = elements[2]
